---
title: "p8105_hw3_qs2260"
author: "hazel"
date: "2022-10-11"
output: github_document
---

```{r}
library(tidyverse)
library(patchwork)
library(dplyr)
library(ggplot2)
library(ggridges)
```
```{r}
qnorm(0.975)
```

# Problem 2

Sum up 24 hour activity
```{r}
tidy_acce = read_csv(file = "data/accel_data.csv")%>% 
  janitor::clean_names()%>%
  mutate(classify = ifelse((day == "Saturday"|day == "Sunday"),"weekend","weekday"))%>%
  mutate(total_act = rowSums(.[4:1443]))
```
made up table and draw plot
```{r}
tidy_df =tidy_acce %>% 
  select(week, day, classify, total_act)%>%
  arrange(total_act)
tidy_gf = tidy_acce %>%
  pivot_longer(activity_1:activity_1440,
               names_to = 'minutes',
               values_to = 'act') %>%
  ggplot(aes(x=as.integer(sub("activity_","",minutes)), y= act, color = day))+
  geom_line(alpha=0.5)

tidy_gf

```
After cleaning the dataset, the tidy_acce table lefts 35 rows and 1445 columns, which contains 1443 varibles includes week, day_id, day and 1440 minutes activity. 

The the table tidy_df shows the total activity of each day, which shows that the week and day is not really related with total activity.

Based on the ggplot result, it can be concluded that the most higher activity are mainly focus on 1200 minutes, and the lowest activity are located at around 200 minutes. 
# Problem 3

```{r}
tidy_noaa = read_csv(file = "data/nynoaadat.csv")%>% 
  janitor::clean_names()%>%
  separate(date, into = c("year", "month", "day"))%>%
  mutate(prcp = prcp / 10 ,
    tmax = as.numeric(tmax) /10,
    tmin = as.numeric(tmin) /10,
    year = as.numeric(year),
    day = as.numeric(day))
  
```

```{r}
names(which.max(table(tidy_noaa$snow)))
```
```{r}
tidy_mon = tidy_noaa%>%
  filter(month == c("01", "07"))%>%
  group_by(id, year, month)%>%
  summarize(ave_tmax = mean(tmax, na.rm=TRUE))%>%
  ggplot(aes(x=year, y=ave_tmax, color=month))+
  geom_point()+
  geom_smooth(alpha=0.5)+
  facet_grid(.~month)
  

tidy_mon
```

```{r}
min_max=ggplot(tidy_noaa, aes(x=tmin, y=tmax))+geom_hex()

snowfall= tidy_noaa%>%
  filter(0< snow, snow<100)%>%
  mutate(year = as.factor(year))%>%
  ggplot(aes(x=snow, color=year))+
  geom_density()

snowfall/min_max
```

